Spatial Analysis

### 2022-01-25 Scripts/spatial_analisis.Rmd
misc.

# Estimate Area
# Degree ressolution for area estimation
# https://rdrr.io/github/stineb/rbeni/src/R/area.R
# https://www.pmel.noaa.gov/maillists/tmap/ferret_users/fu_2004/msg00023.html
# https://www.engr.scu.edu/~emaurer/tools/calc_cell_area_cgi.pl

@@

grids %>% 
  group_by(state,spatial,spp,index,lat,lon) %>%
  tally() %>% 
  # View()
  mutate(
    area = (4 * r_earth^2 * 0.5 * 0.3 * pi/180 * cos(abs(lat) * pi/180 ) * sin(0.5 * 0.3 * pi/180))/1000000
  ) %>% 
  # View()
  group_by(state,spatial,spp) %>%
  summarise(tot_area = sum(area)) %>% 
  select(-spp) %>%
  group_by(state,spatial) %>%
  top_n(1,tot_area) %>%
  group_by(state,spatial) %>%
  summarise(tot_area = mean(tot_area)) %>%
  spread(spatial,tot_area) %>%
  mutate(
    # fp = replace_na(fp,0),
    diff = round((abs(fp-sw))/((fp+sw)/2)*100)
  ) %>% 
  View()

>>>>

# Estimate Area
# Degree ressolution for area estimation
# https://rdrr.io/github/stineb/rbeni/src/R/area.R
# https://www.pmel.noaa.gov/maillists/tmap/ferret_users/fu_2004/msg00023.html
# DOUBLE CHECK RESULTS BELOW
# https://www.engr.scu.edu/~emaurer/tools/calc_cell_area_cgi.pl

@@

grids %>% 
  group_by(state,spatial,spp,index,lat,lon) %>%
  tally() %>% 
  # View()
  mutate(
    area = (4 * r_earth^2 * 0.5 * res_lon * pi/180 * cos(abs(lat) * pi/180 ) * sin(0.5 * res_lon * pi/180))/1000000
  ) %>% 
  # View()
  group_by(state,spatial,spp) %>%
  summarise(tot_area = sum(area)) %>% 
  select(-spp) %>%
  group_by(state,spatial) %>%
  top_n(1,tot_area) %>%
  group_by(state,spatial) %>%
  summarise(tot_area = mean(tot_area)) %>%
  spread(spatial,tot_area) %>%
  mutate(
    # fp = replace_na(fp,0),
    diff = round((abs(fp-sw))/((fp+sw)/2)*100)
  ) %>% 
  View()
